Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-06 docs/paper.tex
Worked on plotting of experiments, set out outline for paper

\documentclass[english]{article}
\usepackage{geometry}
\usepackage{inputenc}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\makeatletter
\usepackage{url}
\makeatother
\usepackage{babel}

@@

	As was shown by Geiger et al. \cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
	Such methods are in general suboptimal so solutions to instances defined for a set shunting yard can be thought of as crudely characterising a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost. 
	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
	Mulderij et al. \cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
	For this to succeed, a way to optimally solve MAPFM instances is needed.

@@

	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts. Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$.

	\section{Extending ICTS with matching} % Your contribution
	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation had to be changed. In regular ICTS, given a MAPF instance with agents $a_1,\ldots,a_k$ with goals $g_1,\ldots,g_k$ starting at locations $s_1,\ldots,s_k$, the root is given by the cost $c_i$ for each agent $a_i$ of the shortest path from $s_i$ to $g_i$, i.e. without taking conflicts into account. Any optimal pathfinding algorithm can be used for this. The root of the ICT then is the vector $(c_1,c_2,\ldots,c_k)$ with $k$ children $(c_1 + 1, c_2,\ldots,c_k), (c_1, c_2 + 1,\ldots,c_k),\ldots,(c_1, c_2,\ldots,c_k + 1)$ so that each component of the parent is incremented by 1 in exactly one child. This child-generation rule holds for all ICT nodes.

@@

	\subsection{Properties of ICTS-m}
	<insert proof>
	\printbibliography

>>>>

\documentclass[english]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{inputenc}
\geometry{verbose,tmargin=3.5cm,bmargin=4cm,lmargin=3.8cm,rmargin=3.8cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\makeatletter
\usepackage{url}
\makeatother
\usepackage{babel}

@@

	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances. 
	Such methods are suboptimal so solutions to instances defined for a set shunting yard can be
 said to characterise a lower bound on the capacity of the shunting yard, as each solution cost gives a (loose) upper-bound for the optimal solution cost. 
	The company, however, is interested in learning tight upper bounds for the capacity of existing shunting yards to inform decisions about infrastructure expansion. 
	Mulderij et al. \cite{mulderij2020} propose the multi-agent pathfinding (MAPF) problem \cite{stern2019} extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation for finding such upper-bounds using an approach analogous to that outlined above.
	For this to succeed, a way to optimally solve MAPFM instances is needed.

@@

	Within each team $t_i$, agent $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution \cite{ma2016}. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no swapping conflicts. Practically, this means that no two agents may be at $v\in V$ at the same timestep and that if agents $i,j$ are at locations $u,v$ respectively at timestep $t$, they may not be at locations $v,u$ at timestep $t+1$. 
	\section{Matching in ICTS} % Your contribution
	Two classes of algorithms were found to solve MAPFM using ICTS-based methods: exhaustively enumerating MAPF instances corresponding to matchings solving these using a variant of regular ICTS, and modifying the increasing cost tree search itself to accomodate for the matching extension. In the following, both

	Increasing Cost Tree Search with Matching (ICTS-m) generalizes ICTS to optimally solve MAPFM instances. Few changes to ICTS were necessary to accomodate for matching in this increasing cost tree scheme. Specifically, the ICT root generation and the MDD generation had to be changed. In regular ICTS, given a MAPF instance with agents $a_1,\ldots,a_k$ with goals $g_1,\ldots,g_k$ starting at locations $s_1,\ldots,s_k$, the root is given by the cost $c_i$ for each agent $a_i$ of the shortest path from $s_i$ to $g_i$, i.e. without taking conflicts into account. Any optimal pathfinding algorithm can be used for this. The root of the ICT then is the vector $(c_1,c_2,\ldots,c_k)$ with $k$ children $(c_1 + 1, c_2,\ldots,c_k), (c_1, c_2 + 1,\ldots,c_k),\ldots,(c_1, c_2,\ldots,c_k + 1)$ so that each component of the parent is incremented by 1 in exactly one child. This child-generation rule holds for all ICT nodes.

@@

	\subsection{Properties of ICTS-m}
	<insert proof>
	\section{Experimental results}
	\section{Responsible Research}
	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project. Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.

	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository \footnote{\url{https://github.com/tbvanderwoude/icts-m}}. Included is also code used to benchmark different configurations of the ICTS solver.

	\section{Discussion}
	\section{Conclusions}
	\section{Future work}
	\printbibliography
